\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-05 introduction.tex

% mention expression problem and family polymorphism solving it
% proof engineering, not being focused, fampoly on proof engineering
% contribution

>>>>

% mention expression problem and family polymorphism solving it
% proof engineering, not being focused, fampoly on proof engineering
% contribution
It is hard to write modular, extensible code.
It is even harder to write modular, extensible proofs.
While there exist many linguistic solutions to code reuse and
extensibility in object-oriented and functional languages,
linguistic solutions are lacking in proof assistants.

Meanwhile, language designers and researchers are increasingly
using proof assistants to mechanize meta\-theories, building on each
other's work.
Therefore, it has become ever more important that proof assistants
make it easy to write reusable, extensible code and proofs.
